R Notebook

### 2018-10-10 analysis/final_analysis.Rmd
make scatter

Look at pattern of predictives for each model, compared to empirical number of features mentioned

```{r}
rbind(read.csv('../modeling/bdaOutput/occlusionSensitivityPredictives.csv') %>% mutate(source = 'occlusion-sensitive model'),
      read.csv('../modeling/bdaOutput/egocentricPredictives.csv') %>% mutate(source = 'occlusion-blind model')) %>%
  mutate(i = row_number()) %>%
  gather(condition, value, close_hidden:far_visible) %>%
  group_by(condition, source) %>%
  summarize(mean = estimate_mode(value),
            ci_lower = round(HPDlo(value), 3),
            ci_upper = round(HPDhi(value), 3)) %>%
  separate(condition, into = c('context', 'hidden')) %>%
  mutate(hidden = ifelse(hidden == 'hidden', 'yes', 'no')) %>%
  rbind(d %>% 
          group_by(context, hidden) %>% 
          tidyboot_mean(column = numFeatures) %>%
          ungroup() %>%
          mutate(context = as.character(context)) %>%
          mutate(source = as.character('empirical data')) %>% 
          select(-empirical_stat, -n)) %>%
  mutate(source = factor(source, levels = c('empirical data', 'occlusion-sensitive model', 
                                            'occlusion-blind model'))) %>%
  ggplot(aes(x = context, fill = hidden, y = mean)) +
    geom_bar(stat = 'identity', position = dodge) +
    geom_errorbar(aes(ymax = ci_upper, ymin = ci_lower), position = dodge, width = 0) +
    facet_wrap(~ source) +
    theme_few() +
    theme(aspect.ratio = 1, text = element_text(size=20)) +
    ylab('mean # features produced')

@@

>>>>

Look at pattern of predictives for each model, compared to empirical number of features mentioned
```{r}
dodge <- position_dodge(width=0.9)

rbind(
    read.csv('../modeling/bdaOutput/occlusionSensitivityPredictives.csv') %>% mutate(source = 'occlusion-sensitive model'),
    read.csv('../modeling/bdaOutput/egocentricPredictives.csv') %>% mutate(source = 'occlusion-blind model')
    ) %>%
  mutate(i = row_number()) %>%
  gather(condition, value, -prob, -MCMCprob, -source, -i) %>%
  separate(condition, sep = '_', into = c('context', 'numDistractors', 'distractorType', 'hidden')) %>%
  group_by(context, hidden, source) %>%
  summarize(mean = estimate_mode(value),
            ci_lower = round(HPDlo(value), 3),
            ci_upper = round(HPDhi(value), 3)) %>%
  #separate(condition, into = c('context', 'hidden')) %>%
  ungroup() %>%
  mutate(hidden = ifelse(hidden == 'hidden', 'yes', 'no')) %>%
  rbind(d %>% 
          group_by(context, hidden) %>% 
          tidyboot_mean(column = numFeatures) %>%
          ungroup() %>%
          mutate(context = as.character(context)) %>%
          mutate(source = as.character('empirical data')) %>% 
          select(-empirical_stat, -n)) %>%
  mutate(source = factor(source, levels = c('empirical data', 'occlusion-sensitive model', 
                                            'occlusion-blind model'))) %>%
  ggplot(aes(x = context, fill = hidden, y = mean)) +
    geom_bar(stat = 'identity', position = dodge) +
    geom_errorbar(aes(ymax = ci_upper, ymin = ci_lower), position = dodge, width = 0) +
    facet_wrap(~ source) +
    theme_few() +
    theme(aspect.ratio = 1, text = element_text(size=20)) +
    ylab('mean # features produced')

@@

```{r}
to.plot <- rbind(read.csv('../modeling/bdaOutput/occlusionSensitivityPredictives.csv') %>% mutate(source = 'occlusion-sensitive model'),
     read.csv('../modeling/bdaOutput/egocentricPredictives.csv') %>% mutate(source = 'occlusion-blind model')
     ) %>%
  mutate(i = row_number()) %>%
  gather(condition, value, -prob, -MCMCprob, -source, -i) %>%
  group_by(condition, source) %>%
  summarize(mean = estimate_mode(value),
            ci_lower = round(HPDlo(value), 3),
            ci_upper = round(HPDhi(value), 3)) %>%
  separate(condition, sep = '_', into = c('context', 'numDistractors', 'distractorType', 'hidden')) %>%
  mutate(hidden = ifelse(hidden == 'hidden', 'yes', 'no')) %>%
  rbind(read_csv('../modeling/bdaInput/bdaInput.csv') %>% 
          mutate(numFeatures = color + shape + texture) %>%
          group_by(context, distractorType, numDistractors, hidden) %>% 
          tidyboot_mean(column = numFeatures) %>%
          ungroup() %>%
          mutate(numDistractors = numDistractors - 2) %>%
          mutate(context = as.character(context)) %>%
          mutate(distractorType = gsub("_", "", distractorType)) %>%
          mutate(source = as.character('empirical data')) %>% 
          ungroup() %>%
          select(-empirical_stat, -n)) %>%
  mutate(source = factor(source, levels = c('empirical data', 'occlusion-sensitive model', 
                                            'occlusion-blind model'))) %>%
  unite(col = asdf, mean, ci_lower, ci_upper) %>%
  spread(source, asdf) %>%
  separate(`empirical data`, sep = '_', into = c('emp_mean', 'emp_lower', 'emp_upper'))%>%
  separate(`occlusion-sensitive model`, sep = '_', into = c('occ_mean', 'occ_lower', 'occ_upper')) %>%
  separate(`occlusion-blind model`, sep = '_', into = c('ego_mean', 'ego_lower', 'ego_upper')) %>%
  mutate(emp_mean = as.numeric(emp_mean), emp_lower = as.numeric(emp_lower), emp_upper = as.numeric(emp_upper),
         occ_mean = as.numeric(occ_mean), occ_lower = as.numeric(occ_lower), occ_upper = as.numeric(occ_upper),
         ego_mean = as.numeric(ego_mean), ego_lower = as.numeric(ego_lower), ego_upper = as.numeric(ego_upper))

ggplot(to.plot, aes(x = occ_mean, y = emp_mean)) +
  geom_point() +#(stat = 'identity', position = dodge) +
  geom_errorbar(aes(ymin = emp_lower, ymax = emp_upper), width = 0) +
  #geom_errorbarh(aes(xmin = occ_lower, xmax = occ_upper), width = 0) +
  geom_smooth(method = 'lm') +
  theme_few() +
  theme(aspect.ratio = 1, text = element_text(size=20)) +
  xlab('predicted # features')+
  ylab('empirical # features')

ggsave('../../pragmatics_of_perspective_taking_tex/pnas_format/figures/predictiveScatter.pdf',
       height = 5, width = 9)
```

```{r}
ggplot(to.plot, aes(x = ego_mean, y = emp_mean)) +
  geom_point() +#(stat = 'identity', position = dodge) +
  geom_errorbar(aes(ymin = emp_lower, ymax = emp_upper), width = 0) +
  #geom_errorbarh(aes(xmin = ego_lower, xmax = ego_upper), width = 0) +
  geom_smooth(method = 'lm') +
  theme_few() +
  theme(aspect.ratio = 1, text = element_text(size=20)) +
  xlab('predicted # features')+
  ylab('empirical # features') 
ggsave('../../pragmatics_of_perspective_taking_tex/pnas_format/figures/egocentricScatter.pdf',
       height = 5, width = 9)
```
